Select-based random access \\ to variable-byte encodings

### 2020-04-25 gradu/msc_english_contents.tex
Adds slightly more text

\section{Rank and Select}
$Rank$ and $select$ are two bit array operations. $Rank_1$(i) gives the number of bits set to 1 in the bit array before index i. $Select_1$(i) gives the index of i-th bit that is set to 1. 
Both operations can be implemented to work in constant time \citep[see, e.g.,][]{gbmp2014sea}. The two methods are related to each other: when used on a bit array 
$B$ = \texttt{0100 1101 \underline{1}011}, $select$(5) returns 8 (underlined) and therefore $rank$(8) returns 4.

>>>>

\section{Rank and Select}
$Rank$ and $select$ are two array operations that are widely used in compressed data structures. $Rank_x$($i$) counts the number of occurences of $x$ before index $i$ in the data. $Select_x$($i$) returns the index of the i-th 
occurence of $x$ in the data. In this thesis, these two operations are assumed to work with a bit array. $Rank_1$($i$) counts the number of bits set to 1 before $i$ and $select_1$($i$) returns the index 
of the i-th bit set to 1. Both operations can be implemented to work in constant time \citep[see, e.g.,][]{gbmp2014sea}. The two methods are related to each other: when used on a bit array 
$B$ = \texttt{0100 1101 \underline{1}011}, $select$(5) returns 8 (underlined) and therefore $rank$(8) returns 4.
